\documentclass{article}    
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{amssymb}

\fancypagestyle{plain}{%
\fancyhf{}%
\lhead{ECS165A SQ18}
\rhead{\today}
\cfoot{Homework 2\\ \thepage\ of \pageref{LastPage} }
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
}

\pagestyle{fancy}
\fancyhf{}
\lhead{ECS165A SQ18}
\rhead{\today}
\cfoot{Homework 2\\ \thepage\ of \pageref{LastPage} }
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

\title{Homework 2}
\author{Name: YOUR NAME HERE\\SID: SID HERE}

\maketitle

Due 11:59PM May 2, 2018. {\bf READ ALL DIRECTIONS VERY CAREFULLY!} 
Submit your tex files along with a generated PDF.
You {\bf MUST} put each problem on a separate page with 1a on the first page, for example 1a will be on page 1 and 1b will be on page 2 (this template is already setup for this). Try to keep each answer to one page. 
You {\bf MUST} put your name and student ID in the provided author section above. {\bf FAILURE TO DO SO MAY RESULT IN NO CREDIT!} 


\section*{Problem 1}
For this problem you will consider following relation and set of FDs:\\
$R(A,B,C,D,E)$\\
$B\rightarrow C$\\
$BE\rightarrow D$\\
$DC\rightarrow E$\\
$DE\rightarrow A$\\

\begin{enumerate}[label=\alph*.]
\item What are the keys of $R$? {\bf (Show your closures)} \\
{\bf \input{prob1a.tex} } \clearpage
\item Show that the set of FDs is a minimal basis; if it is not a minimal basis find a minimal basis for the FDs.\\
{\bf \input{prob1b.tex} } \clearpage
\item What are all of the BCNF violations that follow from the FDs? {\bf (Don't just consider the listed FDs, but all that follow.)} \\
{\bf \input{prob1c.tex} } \clearpage
\item Decompose $R$ into BCNF. For each relation, list the keys, and make sure the set of FDs for each is a minimal basis.\\
{\bf \input{prob1d.tex} } \clearpage
\item What are all of the 3NF violations that follow from the FDs? {\bf (Don't just consider the listed FDs, but all that follow.)} \\
{\bf \input{prob1e.tex} } \clearpage
\item Decompose $R$ into 3NF. For each relation, list the keys, and make sure the set of FDs for each is a minimal basis. \\
{\bf \input{prob1f.tex} } \clearpage
\item What are all of the 4NF MVD violations that follow from the FDs? \\
{\bf \input{prob1g.tex} } \clearpage
\item Decompose $R$ into 4NF. For each relation, list the keys, FDs and MVDs. \\
{\bf \input{prob1h.tex} } \clearpage
\item If you project the relation $R$ onto $S(A,B,C)$ what nontrivial FDs and MVDs hold in $S$? \\
{\bf \input{prob1i.tex} } \clearpage
\end{enumerate}

\section*{Problem 2} 
For this problem you will consider following relation and set of FDs:\\
$Courses(C,T,I,H,R,S,G)$\\
$CT\rightarrow I$\\
$TIH\rightarrow R$\\
$THR\rightarrow C$\\
$THS\rightarrow R$\\
$CTS\rightarrow G$\\

Where $C, T, I, H, R, S,$ and $G$ are the course, term, instructor, hour, room, student, and grade respectively. \\

\begin{enumerate}[label=\alph*.]
\item Use the chase test to prove/disprove that  $CTH\rightarrow G$ holds in Courses.\\
{\bf \input{prob2a.tex} } \clearpage
\item Use the chase test to prove/disprove that  $CTH\rightarrow R$ holds in Courses.\\
{\bf \input{prob2b.tex} } \clearpage
\item Use the chase test to prove/disprove that the proposed decomposition has a lossless join.\\
$R_1(C, T, I, H)$\\
$R_2(C, T, H, R, S)$\\
$R_3(C, T, S, G)$\\
{\bf \input{prob2c.tex} } \clearpage
\item Decompose Courses into 3NF.\\
{\bf \input{prob2d.tex} } \clearpage
\item Which of your relations in 3NF are not in BCNF?\\
{\bf \input{prob2e.tex} } \clearpage
\item Which of your relations in 3NF are not in 4NF?\\
{\bf \input{prob2f.tex} } \clearpage
\end{enumerate}

\section*{Problem 3}
Design a academic genealogy database with one entity set: Academics. An academic's
academic parent is their doctoral advisor, their grandparent is their doctoral
advisor's advisor, etc. There are at least two other signators on a disertation
other than the doctoral advisor. The information to record about academics 
includes their birth name, date of birth, date of death (if deceased), field, 
dissertation title, institution, doctoral advisor, second signer, third signer
and any academic children.\\
{\bf \input{prob3.tex} } \clearpage 

\end{document}